Speeding up decimal multiplication

### 2020-11-22 paper/paper.tex
Update

@@

At first sight, there is not much difference between indexing
$T_\ast[C_1 + j]$ and $t[j \cdot 2^{C_2}]$
in the innermost loop,
where $C_1$ and $C_2$ denote loop-invariant expressions that can be calculated once before the loop.
But on x86 and x86-64, there is difference:
these platforms can encode SIB (scale-index-base) directly in the instruction that dereferences the
pointer, but only for constant scales of 1, 2, 4 and 8 bytes.
This means that, if our field element is 8, 16, 32 or 64 bits long, we can dereference $p[j],$
where $p$ points to $T_\ast[C_1],$ in one instruction; but dereferencing
$t[j \cdot 2^{C_2}],$ where $C_2$ can be anything, requires two instructions: first for the bit
shift and the second for dereferencing.

@@

The x86 and x86-64 platforms provide ``conditional moves'' --- instructions that
store a value in a register conditionally, depending on a flag.
They do not alter control flow and are not subject to branch prediction.
Various versions of ARM have similar capabilities, although differently named.

>>>>

By $x \mymod y,$ where $x \in \mathbb{Z},$ $y \in \mathbb{N} \setminus \{0\},$
we mean $z \in \mathbb{N} \cap [0; y-1]$ such that $z \equiv x \, (\mymod \, y).$

By $x \mydiv y,$ where $x \in \mathbb{N},$ $y \in \mathbb{N} \setminus \{0\},$
we mean $\lfloor x / y \rfloor.$

@@

At first sight, there is not much difference between indexing
$T_\ast[C_1 + j]$ and $t[j \cdot 2^{C_2}]$
in the innermost loop,
where $C_1$ and $C_2$ denote loop-invariant expressions that can be calculated once before the loop.
But on x86 and x86-64 platforms, there \textit{is} a difference:
they can encode SIB (scale-index-base) directly in the instruction that dereferences the
pointer, but only for constant scales of 1, 2, 4 and 8 bytes.
This means that, if our field element is 8, 16, 32 or 64 bits long, we can dereference $p[j],$
where $p$ points to $T_\ast[C_1],$ in one instruction; but dereferencing
$t[j \cdot 2^{C_2}],$ where $C_2$ can be anything, requires two instructions: first for the bit
shift and the second for dereferencing.

@@

The x86-64 platform provides ``conditional moves'' --- instructions that
store a value in a register conditionally, depending on a flag.
They do not alter control flow and are not subject to branch prediction.
Various versions of ARM have similar capabilities, although differently named.
